Generalized Linear Mixed Models

### 2009-04-02 docs/inla/inla.rnw
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@174 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{frame}
\frametitle{Example:bacteria}
<<bacmcmc,fig=false,echo=true>>=
library(glmmBUGS)
bac = glmmBUGS(y ~ trt, effects='ID', family='binomial',data=bacteria, file='modelx.bug')
startingValues = bac$startingValues
source("getInits.R")
library(BRugs)
library(R2WinBUGS)
bacResult = bugs(bac$ragged, getInits, 
	parameters.to.save = names(getInits()),
  model.file="model.bug", n.chain=3, n.iter=100, n.burnin=10, n.thin=2,
                             program="openbugs") 
bacParams = restoreParams(bacResult, bac$ragged)

@@

\begin{frame}
\frametitle{Example: Lung cancer in Ontario}

@@

>>>>

\begin{frame}[fragile]
\frametitle{Example:bacteria}
{\scriptsize
<<bacmcmc,fig=false,echo=true>>=
library(glmmBUGS)
bac = glmmBUGS(y ~ trt, effects='ID', family='bernoulli',data=bacteria, modelFile='modelx.bug')
startingValues = bac$startingValues
source("getInits.R")
library(BRugs)
library(R2WinBUGS)
bacResult = bugs(bac$ragged, getInits, 
	parameters.to.save = names(getInits()),
  n.chain=3, n.iter=100, n.burnin=10, n.thin=2,
  program="openbugs", model.file='modelBac.bug') 
bacParams = restoreParams(bacResult, bac$ragged)

@
}
\end{frame}

\begin{frame}[fragile]
\frametitle{Posterior samples}
<<bacSample,echo=true>>=
hist(bacParams$SDID)
@
\end{frame}

\begin{frame}[fragile]
\frametitle{Parameter estimates}
<<bacpar,fig=false,echo=true>>=
bacSummary = summaryChain(bacParams)
bacSummary$scalars[,c(1:3,5,8)]
bacSummary$RID[1:4,c(1:3,5,8)]

@@

\begin{frame}[fragile]
\frametitle{Did the chiain converge?}
<<bacchain,echo=true>>=
checkChain(bacParams)
@

@@

\begin{frame}[fragile]
\frametitle{Example: Lung cancer in Ontario}
\begin{verbatim}
popDataAdjMat = poly2nb(ontario,row.names=as.character(ontario[["CSDUID"]]))

forBugs = glmmBUGS(formula=observed + logExpected ~ 1,
  effects="CSDUID",   family="poisson", 
  spatial=popDataAdjMat,
  data=ontario@data)
startingValues = forBugs$startingValues
source("getInits.R")

ontarioResult = bugs(forBugs$ragged, getInits, 
  parameters.to.save = names(getInits()),
    model.file="model.bug", n.chain=3, n.iter=50, 
    n.burnin=10, n.thin=2,
      program="winbugs", debug=T)

ontarioParams = restoreParams(ontarioResult, forBugs$ragged)
\end{verbatim}
\end{frame}

\comment(

\comment{
	jpeg('Figures/ontarioCancer.jpg', height=600, width=800)
}

\begin{frame}[fragile]
\frametitle{Predicted cancer rates $E(U_i + V_i|Y)$}
\begin{verbatim}
ontarioSummary = summaryChain(ontarioParams)
ontario = mergeBugsData(popdata, ontarioSummary)
spplot(ontario, "RCSDUID.mean")
\end{verbatim}
\includegraphics[width=0.8\textwidth]{ontarioCancer.jpg}
\end{frame}
